Data Formatting

### 2021-03-31 scripts/data_format.Rmd
fix lagged data

Data
```{r}
here()
data <- read_csv(here("/data/weighted_prev_competence_111220.csv"))
names <- read_csv(here("/data/species_names_ids.csv"))
```

@@

evenness %<>% mutate(J = h/lnS) %>% rowwise()
evenness <- evenness[order(evenness$WetAltID),]
#create new df for ordered sites to test lagged richness and evenness on prevalence
lag_evenness <- evenness[-c(4,14,47,90),] #brute force remove site_months out of sequence
lag_evenness$lag_richness <- c(0)
lag_evenness$lag_J <- c(0)
lag_evenness$lag_cc <- c(0)
lag_evenness$lag_size <- c(0)
for(n in 2:91){
  lag_evenness$lag_richness[n] <- lag_evenness$richness[n-1]
  lag_evenness$lag_J[n] <- lag_evenness$J[n-1]
  lag_evenness$lag_cc[n] <- lag_evenness$cc[n-1]
  lag_evenness$lag_size[n] <- lag_evenness$size[n-1]
}

>>>>

Data
```{r}
here()
data <- read_csv(here("data/weighted_prev_competence_111220.csv"))
names <- read_csv(here("data/species_names_ids.csv"))
```

@@

evenness %<>% mutate(J = h/lnS) %>% rowwise()
evenness <- evenness[order(evenness$WetAltID),]
#create new df for ordered sites to test lagged richness and evenness on prevalence
lag_evenness <- evenness[-c(4,14,47,90),] #brute force remove site_months out of sequence
lag_evenness$lag_richness <- c(0)
lag_evenness$lag_J <- c(0)
lag_evenness$lag_cc <- c(0)
lag_evenness$lag_size <- c(0)
for(n in 2:92){
  lag_evenness$lag_richness[n] <- lag_evenness$richness[n-1]
  lag_evenness$lag_J[n] <- lag_evenness$J[n-1]
  lag_evenness$lag_cc[n] <- lag_evenness$cc[n-1]
  lag_evenness$lag_size[n] <- lag_evenness$size[n-1]
}
